What do incoming university students believe about open science practices in

### 2021-07-30 analysis/Manuscript.Rmd
minimal changes to Rmd

```{r setup, include = FALSE}
library(papaja)
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

```{r qual responses}

# [breadcrumbs] 
 # once qual responses are coded, I will need to return here to 
 # include details about which univrsity the participant is enrolled in
 # name of qualification
 # major [how many are majoring in psyc; NAs; will decide later?]

@@

```{r include = FALSE, evaluate = FALSE}
write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
```
Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").

>>>>

```{r setup, include = FALSE}
library(papaja) #install with devtools1
library(here)
library(tidyverse)
library(finalfit) # to keep trailing zeros & round_tidy
library(psych) #for correlation matrices
library(tidyselect) 
library(psychometric) # for correlation confidence intervals - might not need...
library(broom)

@@

@@

```{r crisis descriptions, eval=FALSE, include=FALSE}
write.csv(data.frame("crisis_text" = df$crisis_text[is.na(df$crisis_text)==FALSE]), "crisis_descriptions.csv")
crisis_descriptions = read.csv("crisis_descriptions_marked.csv") #categorised as accurate or not
```

<!-- This needs another csv file in order to run the code above. Also, revise where the csv file is written to and loaded from.  -->

Participants who indicated they had heard of the replication crisis were asked what "What do you think 'the replication crisis' is"? Of the `r length(df$crisis_text[is.na(df$crisis_text)==FALSE])` participants who answered this question, most provided responses roughly consistent with the conventional interpretation of the term. Example responses included "The crisis where most studies were unable to be replicated when researchers decided to replicate previously done studies" and "Where previously trusted studies have been replicated the results were not able to be replicated". Just `r sum(crisis_descriptions$Accurate == "n")` responses were suggestive of a misunderstanding of the term (e.g., "Plagiaris[m]", "only same results being published").
